Figure 5 - IP-MS

### 2024-08-04 ms_figure_5_ipms.Rmd
Some clean-up, Fig2 and Fig5

# Helper function

@@

@@

    ## cluster the rows (to avoid slow clustering in LinkedCharts)
    dist_mat1 <- dist(heatmap_data_mean, method = "euclidian")
    hclust_avg1 <- hclust(dist_mat1, method = "average")
    heatmap_data_mean_clustered <- heatmap_data_mean[hclust_avg1$order, ]

@@

    ## Volcano plots
    ## -------------------------------------------------------------------------
    ## extract comparisons (include only plate format for Atf1 and untagged)
    volcano_list <- metadata(sce)$testres$tests
    volcano_list <- volcano_list[sub("\\.t", "", colnames(testres$tstat))]
    TFIDs <- names(volcano_list)
    TFnames <- .getProteinNameFromComparison(TFIDs)
    # TFnames <- ifelse(grepl("^SP", TFnames), TFnames, stringr::str_to_title(TFnames))

@@

    ## Total number of interactions
    table(ni_int > 0)

    ## Number of TFs with interactions
    table(colSums(ni_int, na.rm = TRUE) > 0)

    ## Total number of TFs
    ncol(ni_int)

    ## Total number of TF-TF interactions (no self-interactions)
    sum(baitdata$nbrIntMat$nbrTFs_wobait)

    ## Number of TFs involved in these TF-TF interactions
    tmp <- baitdata$nbrIntMat |>
        filter(nbrTFs_wobait > 0)
    length(unique(c(tmp$bait, unlist(strsplit(tmp$TFs, ",")))))

    ## Bilateral interactions
    nbr_bilateral <- tmp |>
        select(bait, TFs) |>
        separate_longer_delim(TFs, delim = ",") |>
        mutate(o1 = paste(bait, TFs, sep = "-"),
               o2 = paste(TFs, bait, sep = "-")) |>
        filter(o1 %in% o2) |>
        nrow()

@@

nbrInteractors <- HeatmapAnnotation(
    which = "column",
    `Number of\ninteractors` = 
        anno_barplot(x = rowSums(as.matrix(baitdata_150$nbrIntMat[colnames(baitdata_150$mat), 
                                                     c("nbrTFs_samefam", 
                                                       "nbrTFs_difffam")])), 
                     gp = gpar(fill = na_color,
                               col = na_color),
                     border = FALSE, bar_width = 1.0,
                     axis_param = list(gp = gpar(fontsize = fs)),
                     width = unit(10, "mm")),
    annotation_name_side = "left",
    annotation_name_rot = 0,
    annotation_name_gp = gpar(fontsize = fl))

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(baitdata_150$mat, stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = nbrInteractors, 
                width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 2.2, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_150$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_150$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_150 <- baitdata_150$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_150 <- ggplot(
    pie_data_150,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nstrict cutoff") + 
    theme_void()
```

@@

nbrInteractors <- HeatmapAnnotation(
    which = "column",
    `Number of\ninteractors` = 
        anno_barplot(x = rowSums(as.matrix(baitdata_150_loose$nbrIntMat[colnames(baitdata_150_loose$mat), 
                                                     c("nbrTFs_samefam", 
                                                       "nbrTFs_difffam")])), 
                     gp = gpar(fill = na_color,
                               col = na_color),
                     border = FALSE, bar_width = 1.0,
                     axis_param = list(gp = gpar(fontsize = fs)),
                     width = unit(10, "mm")),
    annotation_name_side = "left",
    annotation_name_rot = 0,
    annotation_name_gp = gpar(fontsize = fl))

hm1b_loose <- Heatmap(baitdata_150_loose$mat, 
                      cluster_rows = FALSE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(baitdata_150_loose$mat, stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.", 
                      na_col = binary_heatmap_colors["FALSE"],
                      column_title = paste(c("150 mM NaCl", rep(" ", 45)), collapse = ""),
                      row_title = "Transcription factors",
                      column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                      row_title_gp = gpar(fontsize = fl),
                      column_names_gp = gpar(fontsize = fs),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = FALSE, show_column_names = FALSE,
                      use_raster = FALSE, show_heatmap_legend = TRUE, 
                      left_annotation = makeComplexAndDBDAnnotation(
                          baitdata_150_loose$mat, 
                          complexes[c("MBF transcription complex", 
                                      "CCAAT-binding factor complex",
                                      "Atf1-Pcr1")],
                          dbd = dbd, 
                          idmap = idmap),
                      top_annotation = nbrInteractors, 
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                      heatmap_height = unit(h_ipmsHm / 2.2, "mm"), 
                      heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                                  border = "gray10",
                                                  border_gp = gpar(lwd = 0.5)))

@@

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_150_loose$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_150_loose$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_150_loose <- baitdata_150_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_150_loose <- ggplot(
    pie_data_150_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_150_loose$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "150 mM NaCl\nlenient cutoff") + 
    theme_void()
```

@@

rnabinding <- read.delim(params$rnabinders)
keep <- rownames(hmdata_150$tstat) %in% c(rnabinding$PomBaseID, .capitalize(rnabinding$Gene_name))
sum(keep)
hm1rna <- Heatmap(hmdata_150$tstat[keep, ], 
                  cluster_rows = FALSE, 
                  cluster_columns = TRUE, 
                  col = makeHeatmapCol(hmdata_150$tstat, stringency = "high"), 
                  border = TRUE, 
                  border_gp = gpar(lwd = 0.5),
                  name = "Mod.\nt-stat.", 
                  na_col = binary_heatmap_colors["FALSE"],
                  column_names_gp = gpar(fontsize = fs),
                  row_names_gp = gpar(fontsize = fs),
                  show_row_names = TRUE, show_column_names = FALSE,
                  use_raster = FALSE, show_heatmap_legend = TRUE,
                  width = unit(w_ipmsHm, "mm"), # heatmap body width
                  heatmap_height = unit(h_ipmsHm/2, "mm"), # whole heatmap height
                  heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                border = "gray10",
                                border_gp = gpar(lwd = 0.5)))

@@

dnabinding <- read.delim(params$dnabinders)
keep <- rownames(hmdata_150$tstat) %in% c(dnabinding$PomBaseID, .capitalize(dnabinding$Gene_name))
sum(keep)
hm1dna <- Heatmap(hmdata_150$tstat[keep, ], 
                  cluster_rows = FALSE, 
                  cluster_columns = TRUE, 
                  col = makeHeatmapCol(hmdata_150$tstat, stringency = "high"), 
                  border = TRUE, 
                  border_gp = gpar(lwd = 0.5),
                  name = "Mod.\nt-stat.", 
                  na_col = binary_heatmap_colors["FALSE"],
                  column_names_gp = gpar(fontsize = fs),
                  row_names_gp = gpar(fontsize = fs),
                  show_row_names = TRUE, show_column_names = FALSE,
                  use_raster = FALSE, show_heatmap_legend = TRUE,
                  width = unit(w_ipmsHm, "mm"), # heatmap body width
                  heatmap_height = unit(1.5 * h_ipmsHm, "mm"), # whole heatmap height
                  heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                border = "gray10",
                                border_gp = gpar(lwd = 0.5)))

@@

nbrInteractors <- HeatmapAnnotation(
    which = "column",
    `Number of\ninteractors` = 
        anno_barplot(x = rowSums(as.matrix(baitdata_500$nbrIntMat[colnames(baitdata_500$mat), 
                                                     c("nbrTFs_samefam", 
                                                       "nbrTFs_difffam")])), 
                     gp = gpar(fill = na_color,
                               col = na_color),
                     border = FALSE, bar_width = 1.0,
                     axis_param = list(gp = gpar(fontsize = fs)),
                     width = unit(10, "mm")),
    annotation_name_side = "left",
    annotation_name_rot = 0,
    annotation_name_gp = gpar(fontsize = fl))

hm1b2 <- Heatmap(baitdata_500$mat, 
                 cluster_rows = FALSE, 
                 cluster_columns = FALSE, 
                 col = makeHeatmapCol(baitdata_500$mat, stringency = "high"), 
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.", 
                 na_col = binary_heatmap_colors["FALSE"],
                 column_title = paste(c("500 mM NaCl", rep(" ", 45)), collapse = ""),
                 row_title = "Transcription factors",
                 column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                 row_title_gp = gpar(fontsize = fl),
                 column_names_gp = gpar(fontsize = fs),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = FALSE, show_column_names = FALSE,
                 use_raster = FALSE, show_heatmap_legend = TRUE,
                 left_annotation = makeComplexAndDBDAnnotation(
                     baitdata_500$mat, 
                     complexes[c("MBF transcription complex", 
                                 "CCAAT-binding factor complex", "Atf1-Pcr1")], 
                     dbd = dbd, idmap = idmap),
                 top_annotation = nbrInteractors, 
                 width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                 heatmap_height = unit(h_ipmsHm / 2.2, "mm"), # whole heatmap height
                 heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_500$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_500$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_500 <- baitdata_500$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_500 <- ggplot(
    pie_data_500,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nstrict cutoff") + 
    theme_void()
```

```{r}
## Expected fraction of 'same family' pairs
famtbl <- table(baitdata_500_loose$nbrIntMat |>
                    filter(dbdfam != "Other" & 
                               bait != "Untagged") |>
                    pull(dbdfam))
nbait <- sum(baitdata_500_loose$nbrIntMat$bait != "Untagged")
(exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1)))

## Pie chart, within-vs-between DBD family interactions
pie_data_500_loose <- baitdata_500_loose$nbrIntMat |>
    filter(bait != "Untagged") |>
    select(nbrTFs_samefam, nbrTFs_difffam) |>
    pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
    group_by(class) |>
    summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
    mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)
pie_bait_500_loose <- ggplot(
    pie_data_500_loose,
    aes(x = "", y = nbrTF, fill = class)) + 
    geom_col(width = 1) + 
    geom_segment(x = 1.55, xend = 1.55, 
                 y = 0, yend = exp_same * sum(pie_data_500_loose$nbrTF),
                 linewidth = 1.5) + 
    geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
    coord_polar("y", start = 0) + 
    scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                 nbrTFs_difffam = main_colors[5]),
                      labels = c(nbrTFs_samefam = "Same DBD family",
                                 nbrTFs_difffam = "Different DBD family"),
                      name = "") + 
    labs(title = "500 mM NaCl\nlenient cutoff") + 
    theme_void()
```

>>>>

# Helper functions

@@

```{r}
makePie <- function(baitdata, title) {
    ## Expected fraction of 'same family' pairs
    famtbl <- table(baitdata$nbrIntMat |>
                        filter(dbdfam != "Other" & 
                                   bait != "Untagged") |>
                        pull(dbdfam))
    nbait <- sum(baitdata$nbrIntMat$bait != "Untagged")
    exp_same <- sum(famtbl * (famtbl - 1)) / (nbait * (nbait - 1))
    print(paste0("Expected fraction of 'same family' pairs: ", 
                 round(exp_same, digits = 5)))

    ## Pie chart, within-vs-between DBD family interactions
    pie_data <- baitdata$nbrIntMat |>
        filter(bait != "Untagged") |>
        select(nbrTFs_samefam, nbrTFs_difffam) |>
        pivot_longer(everything(), names_to = "class", values_to = "nbrTF") |>
        group_by(class) |>
        summarize(nbrTF = sum(nbrTF), .groups = "drop") |>
        mutate(ypos = sum(nbrTF) - cumsum(nbrTF) + 0.5 * nbrTF)

    ggplot(
        pie_data,
        aes(x = "", y = nbrTF, fill = class)) + 
        geom_col(width = 1) + 
        geom_segment(x = 1.55, xend = 1.55, 
                     y = 0, yend = exp_same * sum(pie_data$nbrTF),
                     linewidth = 1.5) + 
        geom_text(aes(y = ypos, label = nbrTF), size = 7, color = "black") + 
        coord_polar("y", start = 0) + 
        scale_fill_manual(values = c(nbrTFs_samefam = main_colors[3],
                                     nbrTFs_difffam = main_colors[5]),
                          labels = c(nbrTFs_samefam = "Same DBD family",
                                     nbrTFs_difffam = "Different DBD family"),
                          name = "") + 
        labs(title = title) + 
        theme_void()
}
```

@@

    ## cluster the rows (to avoid slow clustering in LinkedCharts)
    dist_mat1 <- dist(heatmap_data_mean, method = "euclidean")
    hclust_avg1 <- hclust(dist_mat1, method = "average")
    heatmap_data_mean_clustered <- heatmap_data_mean[hclust_avg1$order, ]

@@

    ## Volcano plots
    ## -------------------------------------------------------------------------
    ## extract comparisons (include only plate format for Atf1 and untagged)
    volcano_list <- metadata(sce)$testres$tests
    volcano_list <- volcano_list[sub("\\.t", "", colnames(testres$tstat))]
    TFIDs <- names(volcano_list)
    TFnames <- .getProteinNameFromComparison(TFIDs)

@@

    ## TF-TF interactions
    tmp <- baitdata$nbrIntMat |>
        filter(nbrTFs_wobait > 0)

    ## Bilateral TF-TF interactions
    nbr_bilateral <- tmp |>
        select(bait, TFs) |>
        separate_longer_delim(TFs, delim = ",") |>
        mutate(o1 = paste(bait, TFs, sep = "-"),
               o2 = paste(TFs, bait, sep = "-")) |>
        filter(o1 %in% o2) |>
        nrow()

@@

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = makeTFIntAnnotation(baitdata_150), 
                width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 2.2, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

```{r}
pie_bait_150 <- makePie(baitdata = baitdata_150,
                        title = "150 mM NaCl\nstrict cutoff")
```

@@

hm1b_loose <- Heatmap(baitdata_150_loose$mat, 
                      cluster_rows = FALSE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.", 
                      na_col = binary_heatmap_colors["FALSE"],
                      column_title = paste(c("150 mM NaCl", rep(" ", 45)), collapse = ""),
                      row_title = "Transcription factors",
                      column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                      row_title_gp = gpar(fontsize = fl),
                      column_names_gp = gpar(fontsize = fs),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = FALSE, show_column_names = FALSE,
                      use_raster = FALSE, show_heatmap_legend = TRUE, 
                      left_annotation = makeComplexAndDBDAnnotation(
                          baitdata_150_loose$mat, 
                          complexes[c("MBF transcription complex", 
                                      "CCAAT-binding factor complex",
                                      "Atf1-Pcr1")],
                          dbd = dbd, 
                          idmap = idmap),
                      top_annotation = makeTFIntAnnotation(baitdata_150_loose), 
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                      heatmap_height = unit(h_ipmsHm / 2.2, "mm"), 
                      heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                                  border = "gray10",
                                                  border_gp = gpar(lwd = 0.5)))

@@

```{r}
pie_bait_150_loose <- makePie(baitdata = baitdata_150_loose, 
                              title = "150 mM NaCl\nlenient cutoff")
```

@@

rnabinding <- read.delim(params$rnabinders)
keep <- rownames(hmdata_150$tstat) %in% c(rnabinding$PomBaseID, .capitalize(rnabinding$Gene_name))
sum(keep)
hm1rna <- Heatmap(hmdata_150$tstat[keep, ], 
                  cluster_rows = FALSE, 
                  cluster_columns = TRUE, 
                  col = makeHeatmapCol(stringency = "high"), 
                  border = TRUE, 
                  border_gp = gpar(lwd = 0.5),
                  name = "Mod.\nt-stat.", 
                  na_col = binary_heatmap_colors["FALSE"],
                  column_names_gp = gpar(fontsize = fs),
                  row_names_gp = gpar(fontsize = fs),
                  show_row_names = TRUE, show_column_names = FALSE,
                  use_raster = FALSE, show_heatmap_legend = TRUE,
                  width = unit(w_ipmsHm, "mm"), # heatmap body width
                  heatmap_height = unit(h_ipmsHm/2, "mm"), # whole heatmap height
                  heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                border = "gray10",
                                border_gp = gpar(lwd = 0.5)))

@@

dnabinding <- read.delim(params$dnabinders)
keep <- rownames(hmdata_150$tstat) %in% c(dnabinding$PomBaseID, .capitalize(dnabinding$Gene_name))
sum(keep)
hm1dna <- Heatmap(hmdata_150$tstat[keep, ], 
                  cluster_rows = FALSE, 
                  cluster_columns = TRUE, 
                  col = makeHeatmapCol(stringency = "high"), 
                  border = TRUE, 
                  border_gp = gpar(lwd = 0.5),
                  name = "Mod.\nt-stat.", 
                  na_col = binary_heatmap_colors["FALSE"],
                  column_names_gp = gpar(fontsize = fs),
                  row_names_gp = gpar(fontsize = fs),
                  show_row_names = TRUE, show_column_names = FALSE,
                  use_raster = FALSE, show_heatmap_legend = TRUE,
                  width = unit(w_ipmsHm, "mm"), # heatmap body width
                  heatmap_height = unit(1.5 * h_ipmsHm, "mm"), # whole heatmap height
                  heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                border = "gray10",
                                border_gp = gpar(lwd = 0.5)))

@@

hm1b2 <- Heatmap(baitdata_500$mat, 
                 cluster_rows = FALSE, 
                 cluster_columns = FALSE, 
                 col = makeHeatmapCol(stringency = "high"), 
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.", 
                 na_col = binary_heatmap_colors["FALSE"],
                 column_title = paste(c("500 mM NaCl", rep(" ", 45)), collapse = ""),
                 row_title = "Transcription factors",
                 column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                 row_title_gp = gpar(fontsize = fl),
                 column_names_gp = gpar(fontsize = fs),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = FALSE, show_column_names = FALSE,
                 use_raster = FALSE, show_heatmap_legend = TRUE,
                 left_annotation = makeComplexAndDBDAnnotation(
                     baitdata_500$mat, 
                     complexes[c("MBF transcription complex", 
                                 "CCAAT-binding factor complex", "Atf1-Pcr1")], 
                     dbd = dbd, idmap = idmap),
                 top_annotation = makeTFIntAnnotation(baitdata_500), 
                 width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                 heatmap_height = unit(h_ipmsHm / 2.2, "mm"), # whole heatmap height
                 heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

```{r}
pie_bait_500 <- makePie(baitdata = baitdata_500, 
                        title = "500 mM NaCl\nstrict cutoff")

pie_bait_500_loose <- makePie(baitdata = baitdata_500_loose, 
                              title = "500 mM NaCl\nlenient cutoff")
```
